%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\chapter*{Acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents

\emph{A significant portion of this thesis represents joint work with my supervisors Christian Johansen and Ulrich Fahrenberg. They have been instrumental in shaping my ideas of concurrent systems and my view of research in general, and their support and intellectual guidance have made this thesis possible. I am also indebted to my other supervisors, Martin Steffen and Olaf Owe. Thank you for sharing your knowledge, offering advice, and for every one of our helpful discussions.}

\emph{So many others have also offered their help along the way. Among them I would like to thank my brother James for taking the time to listen and for offering his valuable insight and perspective. I would also like to thank Bibek Kabi for all the coffee breaks with insightful conversations while I was in Paris as part of my internship. I am grateful to my fellow students who have never turned me down when I have asked questions. In particular, I want to mention Marius Andresen, Mateusz Zych, Norah Nguyen and Ratan Thapa.}

\emph{I would like to thank my family and friends who have supported me along the way. Thank you so much.}

\emph{Last, but certainly not least. Thank you, Zahra.}

\null\hfill \emph{Christopher A. Trotter,}\\
\null\hfill \emph{November 2018}